---
title: "Kermit Perceptions Rank-Based Tests"
author: "Jessica Jagdeo"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My first message in document (Jess)

Hopefully this works right

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender) 

kermit_hist
```

Jess: Perform rank-based comparisons using Mann-Whitney U and Wilcoxon-Signed Rank

Question: Is there a significant difference in pre-talk ranks of Kermit for male and female respondents?

```{r}

mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

mwu_kermit

# NUll hypothesis: There is NOT a significant difference in ranks for male and female respondents.
# Alternative hypothesis: There IS a significant difference in ranks for male and female respondents.
  
```

"There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05)."

Next question (collaborators):

Is there a significant change in Kermit rankings before and after his Bren talk?

```{r}
# HO: There is not a significant difference in ranks for pre- and post - talk scores

wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

wsr_kermit
```
There is no significant difference in ranks for pre- and post- talk Kermit scores (statistical summary here....)
